\begin{longtable}[ht]{| p{1.5cm} | p{13.5cm} |}
    \caption{Weekly Blog Posts - Jack Barnes}
     \\\hline
     Fall - Week 4 &
     \textbf{Progress:} Since last week, we finished the group problem statement.
     Mostly this was just an update of my submission, since I scored fairly well on it.
     During the week, our team met after Tuesday's and Thursday's lecture to discuss the upcoming tasks.
     Our requirement's document was mostly finished, so I took the lead and finished editing it.
     Mark and Cheng did some research and provided sources for most of the definitions.
     Also got the bibliography working correctly and I think the second draft looks pretty good.
     I briefed the team a little bit about the upcoming assignment, and we are already considering the tech review (draft \#1 due next week).
     \\ & \textbf{Problems:} No major issues. I'm still taking the lead on much of the writing, which is alright but not ideal.
     However, since I'm the most comfortable writing in English it's to be expected.
     \\ & \textbf{Plans:} Next week we have a meeting with our client Stacy, who has also designated herself the technical lead.
     We plan to cover our Requirement's document draft and see if there's any large mistakes or misunderstandings.
     Additionally, we're going to look into the Tech Review document, which is where we need to divide the project into pieces that we can each implement.
     I feel that Stacy's expertise will definitely be an asset at this stage.
     Outside of that, the team will continue to have standup meetings after each Tuesday and Thursday class. \\
     \hline
     Fall - Week 5 &
     \textbf{Progress:} This week we started work on the tech review.
     We met with our client on Monday, as she's our technical lead and brainstormed about ways to split the project up, and what potential technologies that we could review.
     After some deliberation, we came up with 3 distinct parts, UI, Back-end and Deployment.
     On Tuesday after lecture, the group discussed which parts we wanted to be responsible for.
     I am doing the back-end, Mark is doing deployment, and Cheng is doing the UI. We began initial research individually, going from suggestions from our client about potential options.
     \\ & \textbf{Problems:} We did run into some issues with dividing the project so that there would be 3 technologies for each person to research options for.
     But in the end, I think we are all happy with our results.
     \\ & \textbf{Plans:} This weekend we'll continue to work on our tech review and turn our first drafts in on Sunday.
     We haven't scheduled a follow up meeting with our client, but we may looking into doing that depending on the needs of the time.
     Otherwise we'll have a standup meeting after lecture on Tuesday to discuss the next steps.\\
     \hline
     Fall - Week 6 &
     \textbf{Progress:} This week the team worked independently on their Tech Reviews.
     We also have started planning for the Design Document.
     \\ & \textbf{Problems:} No real issues this week, the team met after Tuesday's lecture.
     I was unable to make it to the weekly TA meeting as well due to a prior commitment, but I had no issues or concerns to bring to the TA.
     \\ & \textbf{Plans:} For next week we have a meeting with our client on Wednesday 3-5pm to work on the design document and to go over our technology reviews.
     We may need to reschedule our weekly meeting with the TA, I plan to send an email about it very soon.
     \\
     \hline
     Fall - Week 7 &
     \textbf{Progress:} This week the team began work on the Design Document.
     Draft 1 was due on Tuesday.
     The document outline is in place, and some sections filled out with information from previous documents, but there is still much work to do before the next draft deadline next week.
     We also met with our client on Wednesday to discuss our individually completed tech reviews.
     The meeting was very beneficial and should be able to propel us to a quality second draft.
     \\ & \textbf{Problems:} One problem was finding an available time for the team to meet with the TA.
     As Monday was a holiday, we were unable to meet in person with the Client until Wednesday, which forced us to reschedule with our TA.
     She was very gracious and gave us a large window to meet with her.
     In the end, 2 of the group members were able to meet with the TA, and we were able to relay the information to the missing team member.
     There is still some question about the feasibility of using a federated login into the NetScaler, our client will be working towards getting us a VM instance of the NetScaler software to test.
     We are proceeding as-if it's possible, but documentation is a bit ambiguous.
     \\ & \textbf{Plans:} The plans are to not meet after Thursday's lecture (as we normally would).
     This weekend the group member's will work on the Design Document write-ups for their individual components (How these sections will be sub-sectioned is still up in the air as well).
     We have opted to not schedule a meeting with Stacy (our client) for next week, instead we will work towards the second draft.
     \\
     \hline
     Fall - Week 8 &
     \textbf{Progress:} This week was a little slower with progress, our last meeting with the client left us with some additional research to do and rethinking of some components, as our recommended technologies had some conflicts.
     That said, our design document is now nearly complete and I'm pretty satisfied with the results.
     \\ & \textbf{Problems:} As mentioned in the progress section, our individual tech review assignment left us with conflicting recommendations.
     Thankfully our client was able to guide us in the right direction, and I now believe these conflicts have been resolved.
     \\ & \textbf{Plans:} Our plans for next week are to see if we can update our existing documentation with new versions that better reflect our proposed software as we know it today.
     Once this is done we can send all of our documentation to Stacy for her to review.
     Next week is Thanksgiving and my coursework is fairly heavy for this week, but I'm hopeful this can be done sooner than later.
     \\
     \hline
     Fall - Week 9 &
     \textbf{Progress:} This week we were able to update the problem statement and the requirements document to match the current state of the project and from information from previous meetings with our client.
     We've also outlined the next assignment, our Final Progress Report for Fall term.
     \\ & \textbf{Problems:} No real problems this week, it's a short week (Thanksgiving Holiday) without any assignments due.
     \\ & \textbf{Plans:} We scheduled a meeting with out client on Monday December 2nd to review the current state of our documents, allowing up time to make final changes before the end of the term.
     Over the holiday weekend we may begin work on the final progress report.
     \\
     \hline
     Winter - Week 1 &
     \textbf{Progress:} Over winter break, both my teammates were out of the country and didn't have time to do any work on our project.
     I spent a little time acquiring and running a NetScaler VM.
     This week I spent a little time researching how we should implement our design.
     Cheng and I met on Thursday at the library to discuss our project.
     I pushed the basic npm init stuff to our official repo.
     \\ & \textbf{Problems:} This week it was problematic to find available times to meet.
     I've communicated to my team that I am always available, outside of lecture hours, but still it is difficult to schedule meetings as communication has been poor.
     Another big problem at this point is setting up development environments on the other two member's computers.
     \\ & \textbf{Plans:} I'm looking into solutions, and am mocking up instructions for my team members so that they can have a good workflow as well.
     I'm also exploring other options for development environments for them.
     In regards to meeting, we have tentative plans to meet over the weekend.
     The plan is to get everyone on the same page and refocus on our work with this meeting.
     \\
     \hline
     Winter - Week 2 &
     \textbf{Progress:} This week I met with the TA on Monday and was finally able to meet with both group members on Wednesday.
     I've created a development VM (running Lubuntu 19.10 and Node v13) for us to use.
     We decided this was the best solution to some early issues we were having.
     This lets me provide the best assistance to them and normalizes our environments.
     \\ & \textbf{Problems:} It has been problematic to meet with my group members.
     Also, it has been difficult to start development, as I'm unfamiliar with developing with NodeJS on Windows (which both my group-mates use, and are relying on me to assist).
     We've also needed to complete additional research regarding our workflow, this has slowed down our initial progress.
     \\ & \textbf{Plans:} We are meeting as a team on Saturday @ 3pm.
     I'll be distributing the VM appliances which are setup to develop our project.
     I will also be starting a Jenkins instance on AWS which will perform the CI for our project.
     \\
     \hline
     Winter - Week 3 &
     \textbf{Progress:} Progress has been slow.
     Feels like there's been a bit of a learn curve for the other team members for them to be able to get up to speed.
     I've been tracking the to-dos and working on what I can, which has mostly been research and planning thus far.
     Our team met twice this week to work together, and we have a meeting tomorrow to prioritize our tasks.
     \\ & \textbf{Problems:} As mentioned, progress has been slow.
     There's a lot of working parts to consider before implementing solutions.
     We need to refocus our efforts and break tasks into manageable chunks.
     \\ & \textbf{Plans:} As was recommended by our client originally, and reiterated in lecture, we've chosen to begin keeping a Kanban board.
     We'll be using Jira, as our client originally mentioned.
     In our meeting tomorrow, we'll create tasks and assign them to team members. 
     We will also be discussing code organization, deployment, and be writing tests.
     \\
     \hline
     Winter - Week 4 &
     This week's blog entry appears to be missing from Canvas.
     \\
     \hline
     Winter - Week 5 &
     \textbf{Progress:} Little more progress this week.
     Have designed the CI/CD pipeline and implemented it.
     Got a domain so that we could use https with certificates through AWS.
     There's been a lot of configurations that have taken a lot of time to get right.
     During our 2 weekly meetings, I've been better about assigning specific tasks to my team members, offering my assistance with those tasks when needed.
     Feels like we have a good work flow. Maybe we won't quite be alpha ready by next week, but we are very close.
     \\ & \textbf{Problems:} Previous problems about participation from other team members have mostly disappeared.
     It was difficult to assign tasks when it felt like I was the only person with complete working knowledge of our design, but I've dedicated the extra time needed to include the whole team.
     \\ & \textbf{Plans:} Our poster draft is mostly complete.
     We plan to have a standup meeting after lecture on Tuesday to plan our next meeting and assess our progress.
     I also plan to contact Stacy this week to set up 2 meetings, once in week 7 and another at the end of the term.
     We will also need to update our documentation as our implementation differs from original requirements in a couple places.
     \\
     \hline
     Winter - Week 6 &
     \textbf{Progress:} Not too much progress this week, team members were studying for and taking midterms.
     We had a meeting last Saturday to discuss progress and assign new tasks to the group members.
     \\ & \textbf{Problems:} To me it feels like we've fallen a bit behind.
     I've tried to delegate some tasks with minimal success.
     I'll likely have to complete some extra work beyond my own tasks to get this project completed.
     \\ & \textbf{Plans:} We will be meeting this weekend (Saturday or Sunday) to discuss progress and what to do next.
     I'd like to take some serious time before and after this meeting to bring the project into a fully functional state, and then work on including promised features.
     I look forward to the next week and the extra time that I will have available to put towards the project.
     \\
     \hline
     Winter - Week 7 &
     \textbf{Progress:} I was able to get some work done this week on modifying our deployment method to be more inline with our desired final product.
     The team met this week on Wednesday for about an hour.
     We began to prep our presentation, brainstorming about ideas and discussing what we would talk about during the design review.
     \\ & \textbf{Problems:} Much of our meetings involve discussing work I've completed and figuring out how my team may be able to contribute.
     They don't seem comfortable contributing, and at this point I'm content to continue contributing more in the interest of finishing the project on time.
     \\ & \textbf{Plans:} The team will meet again on Sunday , and most likely once more during the week, to discuss progress and the direction forward.
     \\
     \hline
     Winter - Week 8 &
     \textbf{Progress:} This week some work on routes for the relay-netscaler communication was completed, along with authentication with the admin account.
     Work began on the presentation that will take place next Tuesday.
     The team met on Wednesday and will meet on Sunday as well.
     \\ & \textbf{Problems:} It's been a little overwhelming with the amount of work I need to contribute to the project.
     For the sake of completing the project, I plan to dedicate whatever time I need.
     While the input that I get from my team during meetings is great, it would be nice to get more contributions towards the code.
     \\ & \textbf{Plans:} As stated above, the team will meet on Sunday, and I'll be bringing a functional prototype, which can be shown at the Design Review.
     The team may also choose to meet on Monday if the other members decide they would like more time to prepare.
     \\
     \hline
     Winter - Week 9 &
     \textbf{Progress:} This week our group gave our design review presentation, I think it went fairly well and we were able to get some helpful feedback, which I've been able implement (JSON Schema validation and a TOTP authentication scheme).
     Our client (Stacy) also attended.
     I was able to speak with her briefly afterwards, and was reassured that our progression is going just fine.
     \\ & \textbf{Problems:} There is still a lot to implement, which I've been doing mostly myself, but it is manageable at this point.
     \\ & \textbf{Plans:} Our team will meet over the weekend, and again during next week to discuss progress and the direction of the project.
     We will begin discussing how we want to create our video and the Winter progress report that will be due during finals weeks.
     \\
     \hline
     Winter - Week 10 &
     \textbf{Progress:} This week we were able to get our project into a Beta release state.
     There is still some things to work out before code freeze (such as our final deployment solution), but I'm mostly happy with where the project is as currently.
     \\ & \textbf{Problems:} I've still had some difficulty getting full participation from the team, including being able to schedule a time to meet on Thursday.
     Instead I updated the others through Slack about my progress on the project and the timetable for when I'll be working on the remaining assignments before next Tuesday.
     \\ & \textbf{Plans:} Although it's a bit late to be getting started on the video, and it's accompanying presentation, we will be doing that this weekend.
     Originally I was going to be leaving town for a couple days, but that was cancelled, so I have some additional time to work on the remaining assignments.
     Our team will be working on stuff together, remotely, over the weekend, and in person on Monday before the final turn-in.
     \\
     \hline
\end{longtable}